Dashboard section

### 2022-07-31 Report/Draft Dashboard section.Rmd
Adding missing Excel creation.
Updating and adding notes on report captions.

**Ca. 12 sider med all koden...** (Data reading hører kanskje hjemme et annet sted i rapporten? Eller kanskje som appendix, hvis vi får dårlig plass?)

@@

  widen_excel_test(input$excel$datapath)
})
```

@@

A second function is used for the `fill` parameter in order to (1) ensure that positive numbers are always green, irrespective of the presence of negative numbers, and vice versa, and (2) to use slightly nicer colours than the default ggplot2 ones, making use of the 'Tsimshian' palette from Blake R. Mills' creative [MetBrewer](https://github.com/BlakeRMills/MetBrewer) package.

@@

All the plots based on the Excel data make use of the "Hokusai2" palette from the MetBrewer package; in the case of the revenues plot this is not done using the convenience `scale_fill_met_d()` function but rather the `met.brewer()` function in conjunction with `scale_fill_manual()` as the base palette only contains six colours, but the plot has seven categories. The same function is used to generate the text colour in the 'no information' and 'bad data' plots.

@@

# HTML
available_html <- reactive({
  TRUE
}) |> bindEvent("lederlonn" %in% names(htmldata()))
## Download and parameters -----------------------------------------------------
output$report <- downloadHandler(

  # Based on code in Mastering Shiny
  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

The code in the R Markdown document is very similar to that of the dashboard, but structured in a more conventional way. Data warnings are here text rather than blank plots, and the KPIs are integrated into the text instead of being presented in value boxes.

>>>>

**Ca. 13 sider med all koden...** (Data reading hører kanskje hjemme et annet sted i rapporten? Eller kanskje som appendix, hvis vi får dårlig plass?)

@@

  widen_excel_test(input$excel$datapath)
})

## Creating the primary Excel data frame--------------------------------------
exceldata <- reactive({
  widen_excel(excel_test())
})
```

@@

A second function is used for the `fill` parameter in order to (1) ensure that positive numbers are always green, irrespective of the presence of negative numbers, and vice versa, and (2) to use slightly nicer colours than the default ggplot2 ones, making use of the 'Tsimshian' palette from Blake R. Mills' creative [MetBrewer](https://github.com/BlakeRMills/MetBrewer) package.
```{r}
## scale_fill_green ------------------------------------------------------------
# Function with slightly nicer colours than default; ensuring uniformity; +
# ensuring positive values are always green through a test for the presence of
# FALSE values
scale_fill_green <- function(variable) {
  scale_fill_met_d("Tsimshian",
    direction = ifelse(
      mean(variable,
        na.rm = TRUE
      ) == 1, -1, 1
    )
  )
}
```

@@

All the plots based on the Excel data make use of the colour-blind-friendly "Hokusai2" palette from the MetBrewer package; in the case of the revenues plot this is not done using the convenience `scale_fill_met_d()` function but rather the `met.brewer()` function in conjunction with `scale_fill_manual()` as the base palette only contains six colours, but the plot has seven categories. The same function is used to generate the text colour in the 'no information' and 'bad data' plots.

@@

# HTML
available_html <- reactive({
  TRUE
}) |> bindEvent("lederlonn" %in% names(htmldata()))

## Download and parameters -----------------------------------------------------
output$report <- downloadHandler(

  # Based on code in Mastering Shiny - creating a temporary directory and file
  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

The code in the R Markdown document is very similar to that of the dashboard, but structured in a more conventional way. Data warnings are here text rather than blank plots, and the KPIs are integrated into the text instead of being presented in value boxes. Plot descriptions are included as knitr/LaTeX captions.
